---
title: "Run elodea check"
subtitle: "For: alien-cyprus-checklist"
author:
- Lien Reyserhove
- Sanne Govaert
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
number_sections: yes
toc: yes
toc_depth: 3
toc_float: yes
---
  

# Setup 

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = TRUE)
```

Install required packages:

```{r}
pak::pak("onestop-project/elodea")
```

Load libraries:

```{r message = FALSE}
library(tidyverse)      # To do data science
library(elodea)         # To use elodea
library(here)
```

# Retrieve source data

With elodea you can get the taxonomic and distribution information of a published GBIF checklist.

Here we get the source taxa and distributions from the [Checklist of introduced taxa in Cyprus](https://www.gbif.org/dataset/40344688-4ac9-41c0-abdc-ad4556a76dc0)

```{r}
datasetKey <- "40344688-4ac9-41c0-abdc-ad4556a76dc0"


taxa <- get_taxa(datasetKey)
distributions <- get_distributions(datasetKey)
```

We then filter both taxa and distributions with filter_data(), which returns a list with three data frames: taxa, distributions and notes

```{r}
filtered_taxa <- filter_data(taxa, distributions)
```

Save these files as dataframes:

```{r}
taxa <- filtered_taxa$taxa
distributions <- filtered_taxa$distributions
notes <- filtered_taxa$notes
```

Extract unique observations in notes:

```{r}
notes <- notes %>% distinct()
```

# Save to CSV:

```{r}
write_csv(taxa, here("data", "elodea", "taxa.csv"), na = "")
write_csv(distributions, here("data", "elodea", "distributions.csv"), na = "")
write_csv(notes, here("data", "elodea", "notes.csv"), na = "")
```


